---
title: Sight Word Analysis
author: "Grace Clark"
date: "November 1, 2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Load Packages

library(plyr); library(tidyr); library(data.table); library(lme4); library(lmerTest); library(lsmeans)
library(knitr); library(gridExtra); library(pander); library(extrafont)
library(ggplot2)
library(dplyr)
library(tidyr)
library(gridExtra)
library (car)
library(lme4)
library(lsmeans)
library(xtable)
library(readxl)
library(lattice)
library(misty)
library(effects)
library(psych)
library(nlme) #for mixed effects models
```


```{r data}
#Sightword Identification analysis
data <- read_xlsx("C:/Users/clarkg7/OneDrive - William Paterson University/Desktop/Dissertation/Data/MLM data_SW.xlsx")

#Create conditions with no reference level
data$ortho<-ifelse(data$condition=="plus", .5, -.5)
head(data)
describe(data)

data$phase<-ifelse(data$prepost=="pre", -.5, .5)

#correctly label all variables
data$ortho<-as.factor(data$ortho)
data$Gender<-as.factor(data$Gender)
data$Age<-as.numeric(data$Age)
data$ReadingCG<-as.numeric(data$ReadingCG)
data$Readingint<-as.numeric(data$Readingint)
data$LetterID<-as.numeric(data$LetterID)
data$prepost<-as.factor(data$prepost)
data$phase<-as.factor(data$phase)



#Create centered age field
data$AgeC<-data$Age-mean(data$Age)
head(data)

#Empty model
m0<-glmer(correct~(1|ID), data=data, family=binomial)
summary(m0)
#empty model shows nonsignificant intercept- did not perform signficantly better than chance
#What about for pretest? Posttest?
m1<-glmer(correct~(1|ID)+phase, data=data, family=binomial)
summary(m1)
#intercept not significant (p= 0.138), phase not significant

#to see if ortho has effect 
m2<-glmer(correct~(1|ID)+ortho, data=data, family=binomial)
summary(m2)
#intercept not significant
#no effect of orthography (p =0.768)

#interaction between ortho and phase?
m3<-glmer(correct~(1|ID)+ortho*phase, data=data, family=binomial)
summary(m3)
#intercept not significant, ortho not significant, phase not significant, interaction (p = 0.171) approaching?
plot(allEffects(m3))


#to see if other fixed effects contribute to variance
m4<-glmer(correct~(1|ID)+AgeC, data=data, family=binomial)
summary(m4)
#Age not a significant contributor to correctness (p = 0.7023); intercept approaching significant (p = .0803)

#to see if caregiver reading rating contributes to variance
m5<-glmer(correct~(1|ID)+ReadingCG, data=data, family=binomial)
summary(m5)
#When ran model as numeric, no significant contribution of reading CG (p = 0.782)

#to see if reading interest contributes to variance
m6<-glmer(correct~(1|ID)+Readingint, data=data, family=binomial)
summary(m6)
#when ran as numeric, reading interest not significant contributor to correctness (p = 0.547)

#to see if letter ID skills contributes to variance
m7<-glmer(correct~(1|ID)+LetterID, data=data, family=binomial)
summary(m7)
#Letter ID not a significant contributor to variance (p = 0.187); intercept approaching significance (0.071)


#make a model that includes all dependent variables
m8<-glmer(correct~(1|ID)+phase+ortho+ReadingCG+Readingint+LetterID, data=data, family=binomial)
summary(m8)
#nothing significant
plot(allEffects(m8))
     

#Is there an interaction between the effect of orthography and the effect of reading CG, reading int, or letter ID?
m8<-glmer(correct~(1|ID)+ortho*ReadingCG, data=data, family=binomial)
summary(m8)
#interaction not significant
plot(allEffects(m8))
#higher pretest than post test; higher absent than present across all phases; flat reading CG effect; negative reading interest effect; positive slope for letter ID

m9<-glmer(correct~(1|ID)+ortho*Readingint, data=data, family=binomial)
summary(m9)
#interaction approaching significance and ortho too (ortho p =.07) and interaction (p = 0.622)
plot(allEffects(m9))
plot(allEffects(m9), rescale.axis=F, ylab="Proportion Correct", xlab="Reading Interest", main="Interaction of Reading Interest and Orthography")
#lower reading interest did better in ortho plus condition than higher reading interest???? higher reading interest did better in ortho absent condition than lower reading interest

m10<-glmer(correct~(1|ID)+ortho*LetterID, data=data, family=binomial)
summary(m10)
#No significant interaction
plot(allEffects(m10))
plot(allEffects(m10), rescale.axis=F, ylab="Proportion Correct", xlab="Letter Identification", main="Interaction of Letter Identification and Orthography")
#Higher accuracy for more letter identification skills across both conditions


#compare ortho only model to model with 1 fixed effect (pick reading)
m11<-glmer(correct~(1|ID)+ortho+ReadingCG, data=data, family=binomial)
summary(m11)
#not significant 


m12<-glmer(correct~(1|ID)+ortho+Readingint, data=data, family=binomial)
summary(m12)
#not significant

m13<-glmer(correct~(1|ID)+ortho+LetterID, data=data, family=binomial)
summary(m13)
#not significant

#What about when we remove trials that have no response?
data2 <- read_xlsx("C:/Users/clarkg7/OneDrive - William Paterson University/Desktop/Dissertation/Data/MLM data_SWNR.xlsx")

#Create conditions with no reference level
data2$ortho<-ifelse(data2$condition=="plus", .5, -.5)
head(data2)
describe(data2)
data2$phase<-ifelse(data2$prepost=="pre", -.5, .5)


#correctly label all variables
data2$ortho<-as.factor(data2$ortho)
data2$Gender<-as.factor(data2$Gender)
data2$Age<-as.numeric(data2$Age)
data2$ReadingCG<-as.numeric(data2$ReadingCG)
data2$Readingint<-as.numeric(data2$Readingint)
data2$LetterID<-as.numeric(data2$LetterID)
data2$phase<-as.factor(data2$phase)



#Create centered age field
data2$AgeC<-data2$Age-mean(data2$Age)
head(data2)

#Empty model
m14<-glmer(correct~(1|ID), data=data2, family=binomial)
summary(m14)
#empty model shows nonsignificant intercept- did not perform signficantly better than chance (p = 0.871)

#to see if ortho has effect 
m15<-glmer(correct~(1|ID)+ortho, data=data2, family=binomial)
summary(m15)
#intercept not significant which means did not perform significantly better than chance (p=.760)
#no effect of orthography (p=0.771)
plot(allEffects(m15))
#slightly better in ortho plus condition

m16<-glmer(correct~(1|ID)+phase, data=data2, family=binomial)
summary(m16)
plot(allEffects(m16))
#better in pretest than posttest (boredom???)

m17<-glmer(correct~(1|ID)+ortho*phase, data=data2, family=binomial)
summary(m17)
#nothing significant, interaction p =.164
plot(allEffects(m17))

m18<-glmer(correct~(1|ID)+AgeC, data=data2, family=binomial)
summary(m18)
#very large eigenvalue, rescale
data2$AgeCS<-data2$AgeC/10
m18<-glmer(correct~(1|ID)+AgeCS, data=data2, family=binomial)
summary(m18)
# age not significant (p = .572)

m19<-glmer(correct~(1|ID)+ReadingCG, data=data2, family=binomial)
summary(m19)
#reading cg p = .149
plot(allEffects(m19))
#Higher reading caregiver rating then higher proportion correct

m20<-glmer(correct~(1|ID)+Readingint, data=data2, family=binomial)
summary(m20)
#not significant p = .109
plot(allEffects(m20))
#higher reading interest (taking out letter recognition) did worse in SW recognition

m21<-glmer(correct~(1|ID)+LetterID, data=data2, family=binomial)
summary(m21)
#not significant (p = .945)

#check interactions
m22<-glmer(correct~(1|ID)+ortho*AgeCS, data=data2, family=binomial)
summary(m22)
#not significant

m23<-glmer(correct~(1|ID)+ortho*ReadingCG, data=data2, family=binomial)
summary(m23)
#not significant

m24<-glmer(correct~(1|ID)+ortho*Readingint, data=data2, family=binomial)
summary(m24)
#Significant interaction (p=.0219), ortho significant (0.0208)!
plot(allEffects(m24))
#in ortho absent, flat slope (reading interest doesn't matter); in ortho present (reading interest detrimental???) higher reading interest, lower accuracy in ortho present condition 
m25<-glmer(correct~(1|ID)+Readingint*phase, data=data2, family=binomial)
summary(m25)
#intercept and reading interest signficant 
plot(allEffects(m25))
#in pretest, higher reading interest means do worse; in post-test flat slope
#can't do model with ortho and reading interest and phase because large eigenvalue, asking to rescale- try to rescale reading interest
data2$ReadingintS<-data2$Readingint/10
m26<-glmer(correct~(1|ID)+ortho*ReadingintS*phase, data=data2, family=binomial)
summary(m26)
#still failed to converge and nothing signficant

m27<-glmer(correct~(1|ID)+ortho*LetterID, data=data2, family=binomial)
summary(m27)
#not significant


#TRY analyses with high and low groups instead of 30 different groups for CG and interest; median split
data2(describe)
data2$ReadingCGF<-ifelse(data2$ReadingCG > 42, .5, -.5)
data2$ReadingCGF<-as.factor(data2$ReadingCGF)
m28<-glmer(correct~(1|ID)+ortho*ReadingCGF, data=data2, family=binomial)
summary(m28)
#Not significant interaction
#try with just reading as main effect
m29<-glmer(correct~(1|ID)+ReadingCGF, data=data2, family=binomial)
summary(m29)
#not significant

#Reading interest median split
data2$ReadingintF<-ifelse(data2$Readingint > 23, .5, -.5)
data2$ReadingintF<-as.factor(data2$ReadingintF)
m30<-glmer(correct~(1|ID)+ortho*ReadingintF, data=data2, family=binomial)
summary(m30)
#interaction almost significant (p = .0547)
plot(allEffects(m30))
#higher reading interest do worse in ortho plus condition- need to take out phase and only look at post-test though. Muddling data to include pre-test!

data3 <- read_xlsx("C:/Users/clarkg7/OneDrive - William Paterson University/Desktop/Dissertation/Data/MLM_SWpost.xlsx")
describe(data3)
data3$ReadingintF<-ifelse(data3$Readingint > 23, .5, -.5)
data3$ReadingintF<-as.factor(data3$ReadingintF)



#Create conditions with no reference level
data3$ortho<-ifelse(data3$condition=="plus", .5, -.5)



#correctly label all variables
data3$ortho<-as.factor(data3$ortho)
data3$Gender<-as.factor(data3$Gender)
data3$Age<-as.numeric(data3$Age)
data3$ReadingCG<-as.numeric(data3$ReadingCG)
data3$Readingint<-as.numeric(data3$Readingint)
data3$LetterID<-as.numeric(data3$LetterID)
data3$phase<-as.factor(data3$phase)



#Create centered age field
data3$AgeC<-data3$Age-mean(data3$Age)


m31<-glmer(correct~(1|ID)+ortho*ReadingintF, data=data3, family=binomial)
summary(m31)
#nothing significant anymore. Let's rerun with all dependent variables to see if there is an impact in the post-test. Words should be equivalent in pretest.

m32<-glmer(correct~(1|ID)+ortho, data=data3, family=binomial)
summary(m32)
#ortho not significant in post-test

m33<-glmer(correct~(1|ID)+ReadingCG, data=data3, family=binomial)
summary(m33)
#reading skill not significant in post-test

m34<-glmer(correct~(1|ID)+Readingint, data=data3, family=binomial)
summary(m34)
#not significant in post-test

m35<-glmer(correct~(1|ID)+LetterID, data=data3, family=binomial)
summary(m35)
#not significant in post-test

m36<-glmer(correct~(1|ID)+ortho*ReadingCG, data=data3, family=binomial)
summary(m36)
#not significant in post-test

m37<-glmer(correct~(1|ID)+ortho*Readingint, data=data3, family=binomial)
summary(m37)
#not significant in post-test

m38<-glmer(correct~(1|ID)+ortho*LetterID, data=data3, family=binomial)
summary(m38)
#nothing significant in post-test


#letter ID mean split
data3$LetterIDF<-ifelse(data3$LetterID > 7, .5, -.5)
m39<-glmer(correct~(1|ID)+ortho*LetterIDF, data=data3, family=binomial)
summary(m39)
#not significant
m40<-glmer(correct~(1|ID)+LetterIDF, data=data3, family=binomial)
summary(m40)
#nowhere near significant

#Try removing all participants with low reliability
data4 <- read_xlsx("C:/Users/clarkg7/OneDrive - William Paterson University/Desktop/Dissertation/Data/MLM data_SWlowrel.xlsx")


data4$ortho<-ifelse(data4$condition=="plus", .5, -.5)
data4$Gender<-as.factor(data4$Gender)
data4$Age<-as.numeric(data4$Age)
data4$ReadingCG<-as.numeric(data4$ReadingCG)
data4$Readingint<-as.numeric(data4$Readingint)
data4$LetterID<-as.numeric(data4$LetterID)
data4$ortho<-as.factor(data4$ortho)
data4$prepost<-as.factor(data4$prepost)


m41<-glmer(correct~(1|ID), data=data4, family=binomial)
summary(m41)
#intercept approaching significance (p=0.0727)

m42<-glmer(correct~(1|ID)+ortho, data=data4, family=binomial)
summary(m42)
#nothing significant

m43<-glmer(correct~(1|ID)+prepost, data=data4, family=binomial)
summary(m43)
#not significant

m44<-glmer(correct~(1|ID)+ortho*prepost, data=data4, family=binomial)
summary(m44)
#intercept approaching significance (p = .0841); nothing signficant
plot(allEffects(m44))
#pretest: did better in ortho absent condition than ortho present condition; in post test did better in ortho present condition than ortho absent but wide error bars



#Correlational analysis
data5 <- read_xlsx("C:/Users/clarkg7/OneDrive - William Paterson University/Desktop/Dissertation/Data/Participant overview_Sight Word Study.xlsx")
describe(data5)
corr.test(data5$Age, data5$'Reading_Parent Q')
#r=0.27, p = .14
corr.test(data5$Age, data5$'Letter ID')
#r=0.09, p = .61
corr.test(data5$Age, data5$`Posttest Absent Correct`)
#r= -.31, p = .08
corr.test(data5$Age, data5$`Posttest Present Correct`)
#r=0.02, p = .89
cor.test(data5$`Reading_Parent Q`, data5$`Letter ID`, method=c("spearman"))
#r=.39, p = 0.03
print(corr.test(data5$`Reading_Parent Q`, data5$`Letter ID`),short=FALSE)
#Lower 0.04 upper 0.65 
corr.test(data5$`Difference Absent`, data5$`Difference Present`)
#r =.38, p = 0.03
corr.test(data5$`Reading_Parent Q`, data5$`Posttest Present Correct`)
#r = .03, p = .87
corr.test(data5$`Letter ID`, data5$`Posttest Present Correct`)
#r = .01, p = .94
corr.test(data5$`Difference Present`, data5$`Reading_Parent Q`)
#r = .06, p = .74
corr.test(data5$`Difference Present`, data5$`Letter ID`)
#r = -.14, p = 0.43
corr.test(data5$`Difference Present`, data5$Age)
#r = -.02, p = .89

#T-test check 
t.test(data5$`Difference Absent`, data5$`Difference Present`, paired = TRUE, alternative = "two.sided")
#p = 0.08222, 95 percent CI overlaps with 0
shapiro.test(data5$`Difference Absent`)
shapiro.test(data5$`Difference Present`)
#can assume normal distribution as p > .05 on Shapiro-Wilk normality test. 
car::leveneTest(data5$`Pretest Absent Correct` - data5$`Posttest Absent Correct`, as.factor(data5$`Child ID`))
t.test(data5$`Difference Absent`, data5$`Difference Present`, paired = TRUE, alternative = "less")


# p = .04111; 95 CI -Inf to -0,027


#So if the one-tailed t-test is significant, we might need to look at difference scores for the multilevel model to be significant too. Try changing MLM data format to look at differences

data6 <- read_xlsx("C:/Users/clarkg7/OneDrive - William Paterson University/Desktop/Dissertation/Data/MLM data_SWdiff.xlsx")


data6$ortho<-ifelse(data6$condition=="plus", .5, -.5)
data6$Gender<-as.factor(data6$Gender)
data6$Age<-as.numeric(data6$Age)
data6$ReadingCG<-as.factor(data6$ReadingCG)
data6$Readingint<-as.factor(data6$Readingint)
data6$LetterID<-as.numeric(data6$LetterID)
data6$ortho<-as.factor(data6$ortho)
data6$prepost<-as.factor(data6$prepost)
data6$difference<-as.factor(data6$difference)
data6$ordinal<-as.numeric(data6$ordinal)
data6improve<-as.factor(data6$improve)

#ChatGPT tells me that because the difference variable has 3 outcomes, we have to do a different mlm. Binomial is only if there are 2 factors but we have 3 (-1, 0, 1 difference). Make the family multinomial() and see what happens.
install.packages("nnet")
library(nnet)
# Fit a multinomial logistic regression model
multinom_model <- multinom(difference ~ ortho, data = data6)

# Print model summary
summary(multinom_model)
#unclear output without p values. Not sure how to interpret even when plotted. Seems like a probability of getting a 1, 0, or -1 difference score based on +/- ortho. Higher probability of 1 score in + ortho but no p values to report?
#try with glmer

m1<-glmer(ordinal ~ ortho + (1 | ID), 
      family = poisson, data = data6)

#This doesn't work because there poisson is for count data (e.g., number of times someone comes in a store). Need to do paired t-test because of three possible outcomes in dependent variable. 

m45<-glmer(improve~(1|ID)+ortho, data=data6, family=binomial)
summary(m45)
#Intercept is significant (What does that mean???); Ortho p = 0.0868
plot(allEffects(m45))
#improve 25% in post-test, on average, for ortho+ condition; improve 17% on post-test for ortho absent condition; close to significant!

#Visualizing data
hist(data$ReadingCG)
hist(data$Readingint)
hist(data$LetterID)
hist(data$Age)
hist(data$IDCorrectAbsent)
hist(data$IDCorrectPresent)
hist(data$PerCorrectAbsent)
hist(data$PerCorrectPresent)
hist(data$PerCorrectAbsentNR)
hist(data$PerCorrectPresentNR)


plot(data$ReadingCG, data$PerCorrectPresent, pch=16, cex=1.3, col = "blue", main = "Proportion Correct in Ortho Plus Condition Plotted Against Reading", xlab="Reading", ylab="Proportion Correct")

plot(data$Readingint, data$PerCorrectPresent, pch=16, cex=1.3, col = "blue", main = "Proportion Correct in Ortho Plus Condition Plotted Against Reading Interest", xlab="Reading Interest", ylab="Proportion Correct")

plot(data$LetterID, data$PerCorrectPresent, pch=16, cex=1.3, col = "blue", main = "Proportion Correct in Ortho Plus Condition Plotted Against Letter Identification", xlab="Letter ID", ylab="Proportion Correct")

#bar plot
data2 <- read_xlsx("C:/Users/clarkg7/OneDrive - William Paterson University/Desktop/Dissertation/Data/MLM data.xlsx")
my_sum <- data2 %>%
  group_by(condition) %>%
  summarise( 
    n=n(),
    mean=mean(correct),
    sd=sd(correct)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))

# Standard Error- bar plot of proprotion correct in each condition with standard error bars
ggplot(my_sum) +
  geom_bar( aes(x=condition, y=mean), stat="identity", fill="forestgreen", alpha=0.5) +
  geom_errorbar( aes(x=condition, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.5) +
  ggtitle("Proportion Correct in Post Test Across Conditions")

#do this with age too
describe(data2)
data2$ageC<-ifelse(data2$Age>1284.7, .5, -.5)
my_sum2 <- data2 %>%
  group_by(ageC) %>%
  summarise( 
    n=n(),
    mean=mean(correct),
    sd=sd(correct)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))
View(my_sum2)
ggplot(my_sum2) +
  geom_bar( aes(x=ageC, y=mean), stat="identity", fill="forestgreen", alpha=0.5) +
  geom_errorbar( aes(x=ageC, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.5) +
  ggtitle("Proportion Correct Across Median Split Ages")

#do this with Reading variables too
my_sum3 <- data2 %>%
  group_by(ReadingCGC) %>%
  summarise( 
    n=n(),
    mean=mean(correct),
    sd=sd(correct)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))
View(my_sum3)
ggplot(my_sum3) +
  geom_bar( aes(x=ReadingCGC, y=mean), stat="identity", fill="forestgreen", alpha=0.5) +
  geom_errorbar( aes(x=ReadingCGC, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.5) +
  ggtitle("Proportion Correct Across Median Split Parent Reporting Reading Skills")

data2$ReadingintC<-ifelse(data2$Readingint> 22, .5, -.5)
my_sum4 <- data2 %>%
  group_by(ReadingintC) %>%
  summarise( 
    n=n(),
    mean=mean(correct),
    sd=sd(correct)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))
View(my_sum4)
ggplot(my_sum4) +
  geom_bar( aes(x=ReadingintC, y=mean), stat="identity", fill="forestgreen", alpha=0.5) +
  geom_errorbar( aes(x=ReadingintC, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.5) +
  ggtitle("Proportion Correct Across Median Split Parent Reporting Reading Interest")

data2$LetterIDC<-ifelse(data2$LetterID > 6.92, .5, -.5)
my_sum5 <- data2 %>%
  group_by(LetterIDC) %>%
  summarise( 
    n=n(),
    mean=mean(correct),
    sd=sd(correct)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))
View(my_sum5)
ggplot(my_sum5) +
  geom_bar( aes(x=LetterIDC, y=mean), stat="identity", fill="forestgreen", alpha=0.5) +
  geom_errorbar( aes(x=LetterIDC, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.5) +
  ggtitle("Proportion Correct Across Mean Split Letter Identification")




#Post-hoc analyses of who passes vs who doesn't in ortho + condition
library("gmodels")
library("car")
library("DescTools")
library("ggplot2")
library("qqplotr")
library("dplyr")



#to see if ortho has effect in POSTTEST 
m1<-glmer(correct~(1|ID)+condition, data=data2, family=binomial)
summary(m1)
plot(allEffects(m1), rescale.axis=F, ylab="Proportion Correct", xlab="Orthography Condition", main="Effect of Orthography on Accuracy")


m2<-glmer(correct~(1|ID)+condition*ReadingCG, data=data2, family=binomial)
summary(m2)
plot(allEffects(m2), rescale.axis=F, ylab="Proportion Correct", xlab="Orthography Condition", main="Interaction of Reading Ability and Orthography")

m3<-glmer(correct~(1|ID)+condition*Readingint, data=data2, family=binomial)
summary(m3)
plot(allEffects(m3), rescale.axis=F, ylab="Proportion Correct", xlab="Orthography Condition", main="Interaction of Reading Ability and Orthography")

m4<-glmer(correct~(1|ID)+condition*LetterID, data=data2, family=binomial)
summary(m4)
plot(allEffects(m4), rescale.axis=F, ylab="Proportion Correct", xlab="Orthography Condition", main="Interaction of Letter ID and Orthography")


#Boxplot

#Create ortho with no reference level
data2$ortho<-ifelse(data2$condition=="absent", -.5, .5)
head(data2)

#correctly label all variables
data2$ortho<-as.factor(data2$ortho)
data2$Gender<-as.factor(data2$Gender)
data2$Age<-as.numeric(data2$Age)
data2$ReadingCG<-as.factor(data2$ReadingCG)
data2$Readingint<-as.factor(data2$Readingint)
data2$LetterID<-as.numeric(data2$LetterID)


library(tidyverse)
library(viridis)
library(RColorBrewer)


data6 %>%
  ggplot( aes(x=ortho, y=`difference`, fill=ortho)) +
    geom_boxplot() +
    scale_fill_brewer(type = "seq", palette=2) +
    geom_jitter(color="blue", size=0.4, alpha=0.9) +
  theme(
      legend.position="none",
      plot.title = element_text(size=18)
    ) +
    ggtitle("Difference between Pretest and Posttest in each Condition") +
    xlab("")


#trying multinomial again
require(foreign)
require(nnet)
require(ggplot2)
require(reshape2)
data <- read_xlsx("C:/Users/clarkg7/OneDrive - William Paterson University/Desktop/Dissertation/Data/MLM data_SWdiff.xlsx")

#Create conditions with no reference level
data$ortho<-ifelse(data$condition=="plus", .5, -.5)
head(data)
describe(data)

data$phase<-ifelse(data$prepost=="pre", -.5, .5)

#correctly label all variables
data$ortho<-as.factor(data$ortho)
data$Gender<-as.factor(data$Gender)
data$Age<-as.numeric(data$Age)
data$ReadingCG<-as.numeric(data$ReadingCG)
data$Readingint<-as.numeric(data$Readingint)
data$LetterID<-as.numeric(data$LetterID)
data$prepost<-as.factor(data$prepost)
data$phase<-as.factor(data$phase)
data$nominal<-as.factor(data$nominal)



#Create centered age field
data$AgeC<-data$Age-mean(data$Age)
head(data)

#choose baseline as same outcome
data$nominal <- relevel(data$nominal, ref = "worse")
test <- multinom(nominal ~ ortho, data = data)
summary(test)
z <- summary(test)$coefficients/summary(test)$standard.errors
p<-(1-pnorm(abs(z), 0, 1))*2
p
lpp <- melt(pp.write, id.vars = c("ortho"), value.name = "probability")
ggplot(lpp, aes(x = write, y = probability, colour = ses)) + geom_line() + facet_grid(variable ~
    ., scales = "free")