---
title: Verb Identification Analysis
author: "Grace Clark"
date: "October 18, 2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Load Packages

library(plyr); library(tidyr); library(data.table); library(lme4); library(lmerTest); library(lsmeans)
library(knitr); library(gridExtra); library(pander); library(extrafont)
library(ggplot2)
library(dplyr)
library(tidyr)
library(gridExtra)
library (car)
library(lme4)
library(lsmeans)
library(xtable)
library(readxl)
library(lattice)
library(misty)
library(effects)
library(psych)
library(nlme) #for mixed effects models
```


```{r data}
#Verb Identification analysis
data <- read_xlsx("C:/Users/clarkg7/OneDrive - William Paterson University/Desktop/Dissertation/Data/MLM data.xlsx")

#Create conditions with no reference level
data$ortho<-ifelse(data$condition=="present", .5, -.5)
head(data)
describe(data)


#correctly label all variables
data$ortho<-as.factor(data$ortho)
data$Gender<-as.factor(data$Gender)
data$Age<-as.numeric(data$Age)
data$ReadingCG<-as.factor(data$ReadingCG)
data$Readingint<-as.factor(data$Readingint)
data$LetterID<-as.numeric(data$LetterID)



#Create centered age field
data$AgeC<-data$Age-mean(data$Age)
head(data)

#Empty model
m0<-glmer(correct~(1|ID), data=data, family=binomial)
summary(m0)
#empty model shows nonsignificant intercept- did not perform signficantly better than chance

#to see if ortho has effect 
m1<-glmer(correct~(1|ID)+ortho, data=data, family=binomial)
summary(m1)
#intercept not significant which means did not perform significantly better than chance (approaching significance 0.088)
#no effect of orthography 


#to see if other fixed effects contribute to variance
m2<-glmer(correct~(1|ID)+AgeC, data=data, family=binomial)
summary(m2)
#very large eigenvalue; rescale age
data$AgeCS<-data$AgeC/10
m3<-glmer(correct~(1|ID)+AgeCS, data=data, family=binomial)
summary(m3)
#Age not a significant contributor to correctness (p = 0.1569)

#to see if caregiver reading rating contributes to variance
m4<-glmer(correct~(1|ID)+ReadingCG, data=data, family=binomial)
summary(m4)
#some significant values when ran ReadingCG as factor but what does that mean (e.g., CG rating of 31 signficant but not others- need to figure out how to reference this or change to high and low reading group)
#When ran model as numeric, no significant contribution of reading CG (p = 0.421)

#to see if reading interest contributes to variance
m5<-glmer(correct~(1|ID)+Readingint, data=data, family=binomial)
summary(m5)
#failed to converge- try to rerun as numeric instead of as factor. Some values approaching significance
#when reran as numeric, reading interest not significant contributor to correctness (p = 0.2321)
#change to numeric and see what the mean is to median split the groups.
data$Readingint<-ifelse(data$Readingint >21.67, .5, -.5)
data$Readingint<-as.factor(data$Readingint)
m5<-glmer(correct~(1|ID)+Readingint, data=data, family=binomial)
summary(m5)
#p = .239 for median split reading interest

#to see if letter ID skills contributes to variance
m6<-glmer(correct~(1|ID)+LetterID, data=data, family=binomial)
summary(m6)
#Letter ID not a significant contributor to variance (p = 0.361)


#make a model that includes all dependent variables
m7<-glmer(correct~(1|ID)+AgeCS+ortho+Readingint+LetterID, data=data, family=binomial)
summary(m7)
#nothing significant
plot(allEffects(m7))
     

#Is there an interaction between the effect of orthography and the effect of reading CG, reading int, or letter ID?
m8<-glmer(correct~(1|ID)+ortho*ReadingCG, data=data, family=binomial)
summary(m8)
#interaction not significant
plot(allEffects(m8))
#higher CG ratings, overall more accurate; slightly higher level for ortho absent

m9<-glmer(correct~(1|ID)+ortho*Readingint, data=data, family=binomial)
summary(m9)
#intercept approaching significance; interaction not significant
plot(allEffects(m9))
plot(allEffects(m9), rescale.axis=F, ylab="Proportion Correct", xlab="Reading Interest", main="Interaction of Reading Interest and Orthography")
#higher reading interest did better overall; steeper slope in ortho absent condition

m10<-glmer(correct~(1|ID)+ortho*LetterID, data=data, family=binomial)
summary(m10)
#No significant interaction
plot(allEffects(m10))
plot(allEffects(m10), rescale.axis=F, ylab="Proportion Correct", xlab="Letter Identification", main="Interaction of Letter Identification and Orthography")
#Higher accuracy for more letter identification skills

m11<-glmer(correct~(1|ID)+ortho*AgeCS, data=data, family=binomial)
summary(m11)
plot(allEffects(m11))


#compare ortho only model to model with 1 fixed effect (pick reading)
m11<-glmer(correct~(1|ID)+ortho+ReadingCG, data=data, family=binomial)
summary(m11)
#not significant 


m12<-glmer(correct~(1|ID)+ortho+Readingint, data=data, family=binomial)
summary(m12)
#not significant

m13<-glmer(correct~(1|ID)+ortho+LetterID, data=data, family=binomial)
summary(m13)
#not significant




#What about when we remove trials that have no response?
data2 <- read_xlsx("C:/Users/clarkg7/OneDrive - William Paterson University/Desktop/Dissertation/Data/MLM dataNR.xlsx")

#Create conditions with no reference level
data2$ortho<-ifelse(data2$condition=="present", .5, -.5)
head(data2)
describe(data2)


#correctly label all variables
data2$ortho<-as.factor(data2$ortho)
data2$Gender<-as.factor(data2$Gender)
data2$Age<-as.numeric(data2$Age)
data2$ReadingCG<-as.factor(data2$ReadingCG)
data2$Readingint<-as.factor(data2$Readingint)
data2$LetterID<-as.numeric(data2$LetterID)



#Create centered age field
data2$AgeC<-data2$Age-mean(data2$Age)
head(data2)

#Empty model
m14<-glmer(correct~(1|ID), data=data2, family=binomial)
summary(m14)
#empty model shows nonsignificant intercept- did not perform signficantly better than chance (p = 0.142)

#to see if ortho has effect 
m15<-glmer(correct~(1|ID)+ortho, data=data2, family=binomial)
summary(m15)
#intercept not significant which means did not perform significantly better than chance (approaching significance 0.088)
#no effect of orthography 
plot(allEffects(m15))

m16<-glmer(correct~(1|ID)+AgeC, data=data2, family=binomial)
summary(m16)
#very large eigenvalue, rescale
data2$AgeCS<-data2$AgeC/10
m16<-glmer(correct~(1|ID)+AgeCS, data=data2, family=binomial)
summary(m16)
# age not significant

m17<-glmer(correct~(1|ID)+ReadingCG, data=data2, family=binomial)
summary(m17)
#some values are significant (CG31, 42, 43, 48, 49)
plot(allEffects(m17))
#make it numeric and see what it looks like
data2$ReadingCG<-as.numeric(data2$ReadingCG)
#not significant

m18<-glmer(correct~(1|ID)+Readingint, data=data2, family=binomial)
summary(m18)
#some values are significant (Int22, 23)
plot(allEffects(m18))
#make it numeric and see what it looks like
data2$Readingint<-as.numeric(data2$Readingint)
#not significant

m19<-glmer(correct~(1|ID)+LetterID, data=data2, family=binomial)
summary(m19)
#not significant

#check interactions
m20<-glmer(correct~(1|ID)+ortho*AgeCS, data=data2, family=binomial)
summary(m20)
#not significant

m21<-glmer(correct~(1|ID)+ortho*ReadingCG, data=data2, family=binomial)
summary(m21)
#not significant

m22<-glmer(correct~(1|ID)+ortho*Readingint, data=data2, family=binomial)
summary(m22)
#not significant

m23<-glmer(correct~(1|ID)+ortho*LetterID, data=data2, family=binomial)
summary(m23)
#not significant


#TRY analyses with high and low groups instead of 30 different groups for CG and interest; median split
data$ReadingCGF<-ifelse(data$ReadingCG > 44.5, .5, -.5)
m24<-glmer(correct~(1|ID)+ortho*ReadingCGF, data=data, family=binomial)
summary(m24)
#Not significant interaction
#try with just reading as main effect
m25<-glmer(correct~(1|ID)+ReadingCGF, data=data, family=binomial)
summary(m25)
#not significant

#Reading interest median split
data$ReadingintF<-ifelse(data$Readingint > 22, .5, -.5)
m26<-glmer(correct~(1|ID)+ortho*ReadingintF, data=data, family=binomial)
summary(m26)
m27<-glmer(correct~(1|ID)+ReadingintF, data=data, family=binomial)
summary(m27)
#not significant

#letter ID mean split
data$LetterIDF<-ifelse(data$LetterID > 6.92, .5, -.5)
m28<-glmer(correct~(1|ID)+ortho*LetterIDF, data=data, family=binomial)
summary(m28)
m29<-glmer(correct~(1|ID)+LetterIDF, data=data, family=binomial)
summary(m29)
#nowhere near significant

#Try removing all participants with low reliability
data <- read_xlsx("C:/Users/clarkg7/OneDrive - William Paterson University/Desktop/Dissertation/Data/MLM data remove low reliability.xlsx")
m30<-glmer(correct~(1|ID), data=data, family=binomial)
summary(m30)

m31<-glmer(correct~(1|ID)+ortho, data=data, family=binomial)
summary(m31)
#still nothing is significant. Intercept approaching significance in empty model

#HOW DO YOU CHECK FOR ORDER EFFECTS?
#added order column and assigned 1 for ortho present first and 0 for ortho absent first
data <- read_xlsx("C:/Users/clarkg7/OneDrive - William Paterson University/Desktop/Dissertation/Data/MLM data.xlsx")
data$ortho<-ifelse(data$condition=="present", .5, -.5)
data$ortho<-as.factor(data$ortho)
data$Gender<-as.factor(data$Gender)
data$Age<-as.numeric(data$Age)
data$ReadingCG<-as.numeric(data$ReadingCG)
data$Readingint<-as.numeric(data$Readingint)
data$LetterID<-as.numeric(data$LetterID)
data$order<-as.factor(data$order)

m32<-glmer(correct~(1|ID)+order, data=data, family=binomial)
summary(m32)
#order not significant (p = 0.205)
m33<-glmer(correct~(1|ID)+ortho+order, data=data, family=binomial)
summary(m33)

#Try with only first 30 participants
data <- read_xlsx("C:/Users/clarkg7/OneDrive - William Paterson University/Desktop/Dissertation/Data/MLM data first 30.xlsx")
head(data)
data$ortho<-ifelse(data$condition=="present", .5, -.5)

data$ortho<-as.factor(data$ortho)
data$Gender<-as.factor(data$Gender)
data$Age<-as.numeric(data$Age)
data$ReadingCG<-as.numeric(data$ReadingCG)
data$Readingint<-as.numeric(data$Readingint)
data$LetterID<-as.numeric(data$LetterID)
data$order<-as.factor(data$order)

m33<-glmer(correct~(1|ID)+ortho, data=data, family=binomial)
summary(m33)
#Intercept is now significant, participants did better than chance; ortho (p = 0.1336)

m34<-glmer(correct~(1|ID)+ortho*ReadingCG, data=data, family=binomial)
summary(m34)
#ReadingCG approaching significance (p = 0.0781)

m35<-glmer(correct~(1|ID)+ReadingCG, data=data, family=binomial)
summary(m35)
#Not significant by itself (p = 0.0886)

m36<-glmer(correct~(1|ID)+Readingint, data=data, family=binomial)
summary(m36)
#p = 0.0717

m37<-glmer(correct~(1|ID)+ortho*Readingint, data=data, family=binomial)
summary(m37)
#reading interest is significant (p = 0.0416) but not interaction

m38<-glmer(correct~(1|ID)+LetterID, data=data, family=binomial)
summary(m38)
#not significant (p = 0.1539)

m39<-glmer(correct~(1|ID)+ortho*LetterID, data=data, family=binomial)
summary(m39)
#nothing significant

m40<-glmer(correct~(1|ID)+order, data=data, family=binomial)
summary(m40)

m41<-glmer(correct~(1|ID)+ortho*order, data=data, family=binomial)
summary(m41)
#nothing significant

#Correlational analysis
data <- read_xlsx("C:/Users/clarkg7/OneDrive - William Paterson University/Desktop/Dissertation/Data/Participant overview.xlsx")
describe(data)
corr.test(data$Age, data$ReadingCG)
#r=0.11
corr.test(data$Age, data$LetterID)
#r=0.19 
corr.test(data$Age, data$IDCorrectAbsent)
#r=0.16
corr.test(data$Age, data$IDCorrectPresent)
#r=0.21
print(corr.test(data$Age, data$LetterID),short=FALSE) 
corr.test(data$Age, data$LetterID, use="pairwise")
#r=0.19
cor.test(data$ReadingCG, data$LetterID, method=c("spearman") )
#rho = 0.44 (p = 0.002)
print(corr.test(data$ReadingCG, data$LetterID),short=FALSE)
#Lower 0.37 upper 0.75 (p =0)
corr.test(data$ReadingCG, data$Readingint)
#r =.64 (p = 0) lower CI 0.44, upper CI 0.78
corr.test(data$Readingint, data$LetterID)
#r = 0.33 (p = 0.02), lower CI 0.06, upper CI 0.56
corr.test(data$ReadingCG, data$PerCorrectPresent)
#r = .17 (p = 0.24)
corr.test(data$Readingint, data$PerCorrectPresent)
#r = .1 (p = .49)
corr.test(data$LetterID, data$PerCorrectPresent)
#r = .15 (p = 0.31)
#also checked against PerCorrectAbsent and nothing significant; also checked NR results and NS

#T-test check 
t.test(data$PerCorrectAbsent, data$PerCorrectPresent, paired = TRUE, alternative = "two.sided")
#p = 0.4588, 95 percent CI overlaps with 0
t.test(data$PerCorrectAbsent, data$PerCorrectPresent, paired = TRUE, alternative = "less")

t.test(data$PerCorrectAbsentNR, data$PerCorrectPresentNR, paired = TRUE, alternative = "two.sided")
#p = 0.1036, 95 percent CI overlaps with 0
t.test(data$PerCorrectAbsentNR, data$PerCorrectPresentNR, paired = TRUE, alternative = "less")
#p = 0.05178, t = -1.6587 (mean difference -7.67)

t.test(data$IDCorrectPresent, data$IDCorrectAbsent, paired = TRUE, alternative = "greater")
#p-test is just half of two tailed



#Visualizing data
hist(data$ReadingCG)
hist(data$Readingint)
hist(data$LetterID)
hist(data$Age)
hist(data$IDCorrectAbsent)
hist(data$IDCorrectPresent)
hist(data$PerCorrectAbsent)
hist(data$PerCorrectPresent)
hist(data$PerCorrectAbsentNR)
hist(data$PerCorrectPresentNR)


plot(data$ReadingCG, data$PerCorrectPresent, pch=16, cex=1.3, col = "blue", main = "Proportion Correct in Ortho Plus Condition Plotted Against Reading", xlab="Reading", ylab="Proportion Correct")

plot(data$Readingint, data$PerCorrectPresent, pch=16, cex=1.3, col = "blue", main = "Proportion Correct in Ortho Plus Condition Plotted Against Reading Interest", xlab="Reading Interest", ylab="Proportion Correct")

plot(data$LetterID, data$PerCorrectPresent, pch=16, cex=1.3, col = "blue", main = "Proportion Correct in Ortho Plus Condition Plotted Against Letter Identification", xlab="Letter ID", ylab="Proportion Correct")

#bar plot
data2 <- read_xlsx("C:/Users/clarkg7/OneDrive - William Paterson University/Desktop/Dissertation/Data/MLM data.xlsx")
my_sum <- data2 %>%
  group_by(condition) %>%
  summarise( 
    n=n(),
    mean=mean(correct),
    sd=sd(correct)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))

# Standard Error- bar plot of proprotion correct in each condition with standard error bars
ggplot(my_sum) +
  geom_bar( aes(x=condition, y=mean), stat="identity", fill="forestgreen", alpha=0.5) +
  geom_errorbar( aes(x=condition, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.5) +
  ggtitle("Proportion Correct in Post Test Across Conditions")

#do this with age too
describe(data2)
data2$ageC<-ifelse(data2$Age>1284.7, .5, -.5)
my_sum2 <- data2 %>%
  group_by(condition, ageC) %>%
  summarise( 
    n=n(),
    mean=mean(correct),
    sd=sd(correct)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))
View(my_sum2)
ggplot(my_sum2) +
  geom_bar( aes(x=ageC, y=mean), stat="identity", fill="forestgreen", alpha=0.5) +
  geom_errorbar( aes(x=ageC, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.5) +
  ggtitle("Proportion Correct Across Median Split Ages")

#do this with Reading variables too
my_sum3 <- data2 %>%
  group_by(ReadingCGC) %>%
  summarise( 
    n=n(),
    mean=mean(correct),
    sd=sd(correct)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))
View(my_sum3)
ggplot(my_sum3) +
  geom_bar( aes(x=ReadingCGC, y=mean), stat="identity", fill="forestgreen", alpha=0.5) +
  geom_errorbar( aes(x=ReadingCGC, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.5) +
  ggtitle("Proportion Correct Across Median Split Parent Reporting Reading Skills")

data2$ReadingintC<-ifelse(data2$Readingint> 22, .5, -.5)
my_sum4 <- data2 %>%
  group_by(condition, ReadingintC) %>%
  summarise( 
    n=n(),
    mean=mean(correct),
    sd=sd(correct)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))
View(my_sum4)
ggplot(my_sum4) +
  geom_bar( aes(x=ReadingintC, y=mean), stat="identity", fill="forestgreen", alpha=0.5) +
  geom_errorbar( aes(x=ReadingintC, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.5) +
  ggtitle("Proportion Correct Across Median Split Parent Reporting Reading Interest")

data2$LetterIDC<-ifelse(data2$LetterID > 6.92, .5, -.5)
my_sum5 <- data2 %>%
  group_by(condition, LetterIDC) %>%
  summarise( 
    n=n(),
    mean=mean(correct),
    sd=sd(correct)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))
View(my_sum5)
ggplot(my_sum5) +
  geom_bar( aes(x=LetterIDC, y=mean), stat="identity", fill="forestgreen", alpha=0.5) +
  geom_errorbar( aes(x=LetterIDC, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.5) +
  ggtitle("Proportion Correct Across Mean Split Letter Identification")




#Post-hoc analyses of who passes vs who doesn't in ortho + condition
library("gmodels")
library("car")
library("DescTools")
library("ggplot2")
library("qqplotr")
library("dplyr")



#to see if ortho has effect in POSTTEST 
m1<-glmer(correct~(1|ID)+condition, data=data2, family=binomial)
summary(m1)
plot(allEffects(m1), rescale.axis=F, ylab="Proportion Correct", xlab="Orthography Condition", main="Effect of Orthography on Accuracy")


m2<-glmer(correct~(1|ID)+condition*ReadingCG, data=data2, family=binomial)
summary(m2)
plot(allEffects(m2), rescale.axis=F, ylab="Proportion Correct", xlab="Orthography Condition", main="Interaction of Reading Ability and Orthography")

m3<-glmer(correct~(1|ID)+condition*Readingint, data=data2, family=binomial)
summary(m3)
plot(allEffects(m3), rescale.axis=F, ylab="Proportion Correct", xlab="Orthography Condition", main="Interaction of Reading Ability and Orthography")

m4<-glmer(correct~(1|ID)+condition*LetterID, data=data2, family=binomial)
summary(m4)
plot(allEffects(m4), rescale.axis=F, ylab="Proportion Correct", xlab="Orthography Condition", main="Interaction of Letter ID and Orthography")


#Boxplot

#Create ortho with no reference level
data2$ortho<-ifelse(data2$condition=="absent", -.5, .5)
head(data2)

#correctly label all variables
data2$ortho<-as.factor(data2$ortho)
data2$Gender<-as.factor(data2$Gender)
data2$Age<-as.numeric(data2$Age)
data2$ReadingCG<-as.factor(data2$ReadingCG)
data2$Readingint<-as.factor(data2$Readingint)
data2$LetterID<-as.numeric(data2$LetterID)


library(tidyverse)
library(viridis)
library(RColorBrewer)

data2 <- read_xlsx("C:/Users/clarkg7/OneDrive - William Paterson University/Desktop/Dissertation/Data/MLM data.xlsx")
data2 %>%
  ggplot( aes(x=ortho, y=`proportion correctNR`, fill=ortho)) +
    geom_boxplot() +
    scale_fill_brewer(type = "seq", palette=2) +
    geom_jitter(color="blue", size=0.4, alpha=0.9) +
  theme(
      legend.position="none",
      plot.title = element_text(size=18)
    ) +
    ggtitle("Proportion Correct in Each Condition") +
    xlab("")

data2 %>%
  ggplot( aes(x=ortho, y=`proportioncorrect`, fill=ortho)) +
    geom_boxplot() +
    scale_fill_brewer(type = "seq", palette=2) +
    geom_jitter(color="blue", size=0.4, alpha=0.9) +
  theme(
      legend.position="none",
      plot.title = element_text(size=18)
    ) +
    ggtitle("Proportion Correct in Each Condition") +
    xlab("")

#determine binomial probability
successes <- 7
total_questions <- 8

# Perform binomial test
binom_test_result <- binom.test(successes, total_questions, p = 1/2, alternative = "greater")

# Print results
print(binom_test_result)



#Verb Identification analysis- correct answers only
data <- read_xlsx("C:/Users/clarkg7/OneDrive - William Paterson University/Desktop/Dissertation/Data/MLM data_correct.xlsx")

#Create conditions with no reference level
data$ortho<-ifelse(data$condition=="present", .5, -.5)
head(data)
describe(data)


#correctly label all variables
data$ortho<-as.factor(data$ortho)
data$Gender<-as.factor(data$Gender)
data$Age<-as.numeric(data$Age)
data$ReadingCG<-as.factor(data$ReadingCG)
data$Readingint<-as.factor(data$Readingint)
data$LetterID<-as.numeric(data$LetterID)



#Create centered age field
data$AgeC<-data$Age-mean(data$Age)
head(data)

#this doesn't work because the outcome variable is a constant. Makes sense. Might do correlations but don't think that will work because of ordinal variables. 

#look at post-hoc analysis with responders and non-responders
data <- read_xlsx("C:/Users/clarkg7/OneDrive - William Paterson University/Desktop/Dissertation/Data/MLM data.xlsx")
my_sum <- data %>%
  group_by(facilitation) %>%
  summarise( 
    n=n(),
    mean=mean(correct),
    sd=sd(correct)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))
View(my_sum)

my_sum2 <- data %>%
  group_by(condition, facilitation) %>%
  summarise( 
    n=n(),
    mean=mean(correct),
    sd=sd(correct)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))
View(my_sum2)

my_sum3 <- data %>%
  group_by(condition, facilitationNR) %>%
  summarise( 
    n=n(),
    mean=mean(correct),
    sd=sd(correct)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))
View(my_sum3)

my_sum4 <- data %>%
  group_by(facilitationNR) %>%
  summarise( 
    n=n(),
    mean=mean(Readingint),
    sd=sd(Readingint)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))
View(my_sum4)

my_sum5 <- data %>%
  group_by(facilitationNR) %>%
  summarise( 
    n=n(),
    mean=mean(LetterID),
    sd=sd(LetterID)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))
View(my_sum5)

my_sum6 <- data %>%
  group_by(facilitationNR) %>%
  summarise( 
    n=n(),
    mean=mean(Age),
    sd=sd(Age)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))
View(my_sum6)

my_sum7 <- data %>%
  group_by(facilitation) %>%
  summarise( 
    n=n(),
    mean=mean(Age),
    sd=sd(Age)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))
View(my_sum7)

my_sum8 <- data %>%
  group_by(facilitation) %>%
  summarise( 
    n=n(),
    mean=mean(LetterID),
    sd=sd(LetterID)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))
View(my_sum8)

my_sum9 <- data %>%
  group_by(facilitation) %>%
  summarise( 
    n=n(),
    mean=mean(Readingint),
    sd=sd(Readingint)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))
View(my_sum9)


#Removed those that failed warmup or didn't respond to any trails
data <- read_xlsx("C:/Users/clarkg7/OneDrive - William Paterson University/Desktop/Dissertation/Data/MLM data_fail.xlsx")

#Create conditions with no reference level
data$ortho<-ifelse(data$condition=="present", .5, -.5)
head(data)
describe(data)


#correctly label all variables
data$ortho<-as.factor(data$ortho)
data$Gender<-as.factor(data$Gender)
data$Age<-as.numeric(data$Age)
data$ReadingCG<-as.factor(data$ReadingCG)
data$Readingint<-as.factor(data$Readingint)
data$LetterID<-as.numeric(data$LetterID)



#Create centered age field
data$AgeC<-data$Age-mean(data$Age)
head(data)

#Empty model
m0<-glmer(correct~(1|ID), data=data, family=binomial)
summary(m0)
#empty model intercept NS

#to see if ortho has effect 
m1<-glmer(correct~(1|ID)+ortho, data=data, family=binomial)
summary(m1)
#intercept NS, ortho NS


#to see if other fixed effects contribute to variance
m2<-glmer(correct~(1|ID)+AgeC, data=data, family=binomial)
summary(m2)
#very large eigenvalue; rescale age
data$AgeCS<-data$AgeC/10
m3<-glmer(correct~(1|ID)+AgeCS, data=data, family=binomial)
summary(m3)
#Age NS

#to see if reading interest contributes to variance
m5<-glmer(correct~(1|ID)+Readingint, data=data, family=binomial)
summary(m5)
#failed to converge- try to rerun as numeric instead of as factor. Some values approaching significance
#when reran as numeric, reading interest NS

#to see if letter ID skills contributes to variance
m6<-glmer(correct~(1|ID)+LetterID, data=data, family=binomial)
summary(m6)
#Letter ID NS

#interaction check
m7<-glmer(correct~(1|ID)+ortho*LetterID, data=data, family=binomial)
summary(m7)
#all factors and interactions NS

m8<-glmer(correct~(1|ID)+ortho*Readingint, data=data, family=binomial)
summary(m8)
#all factors and interactions NS

m9<-glmer(correct~(1|ID)+ortho*AgeCS, data=data, family=binomial)
summary(m9)
#all factors and interactions NS